---
title: "Examen"
author: "Orlando"
date: "14/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("tidyverse")
```

## Pregunta 1

1.- Create a numeric vector that contains the months of a year. Then, create another vector containing the name for each month. Later, you should assign the months and names. Finally, you should select and display the months related to the summer season (June, July, August)

```{r vector}
num <- c(1,2,3,4,5,6,7,8,9,10,11,12)
nameM <- c("January", "February", "March","April", "May","June", "July", "August", "September", "October", "November", "December" )

named<-`names<-`(num,nameM)

named[6:8]

```


## Pregunta 2

Construct a matrix with 5 rows containing the numbers 1 up to 15, filled row-wise.

```{r Matrix}
vecnum <- c(1:15)
matnum <- matrix(vecnum, nrow = 3, byrow = TRUE)
matnum
```

## Pregunta 3

Create a factor with these observations "XXL", "XXL", "XXL", "XL", "L", "M", "M", "S", "S", "S" and print a summary

```{r}
vecf <- c("XXL", "XXL", "XXL", "XL", "L", "M", "M", "S", "S", "S")
Fact <- factor(vecf)
summary(Fact)
```

## Pregunta 4

 Create and print a data frame that should contain:

5 of your courses (e.g. Fundamentals of Programming, Object-Oriented Programming, Databases, etc ).
5 of your marks
5 of your professors' names

```{r}
courses <-c("Interaccion Humano Computadora - IHM", "Topicos Selectos de Ingenieria de Software", "Metricas de Software", "Arquitectura de las computadoras", "Graficacion")
marks <-c(8.5,7,8,8.7,10)
prof<- c("Fransisco Lopez", "Alan Ponce", "Abrham Lopez", "Oscar?", "Maritza")

data <- data.frame(courses,marks,prof)

data

```

## Pregunta 5

Load the dataset labeled as ITU_WB.csv that is located in the data folder and storage this dataset in a variable called itu. Then, you should describe the composition of the dataset. This description must contain the number of observations, variables and the type of each variable

un total de 12 variables/columnas, las cuales son num(tipo int), Economy(tipo factor), Code(tipo factor), Region(tipo factor), Income.Group(tipo factor), year(tipo int), Internet.value(tipo num), Total.population(tipo int), "GDP..US.."(tipo num), "Life.Expectancy..Years."(tipo num),"GDP.per.capita.income" y "Fertility..Births.per.woman"(tipo num), con un total de 3735 obervaciones.


```{r}
itu <- read.csv("~/conexion a git/ts_2019_2/data/ITU_WB.csv")

summary(itu)

itu

```


## Pregunta 6

Filter the itu dataset to retrieve only the observation from Mexico, grouped by year and in descending order selecting the "Internet value" column

```{r}

```


## Pregunta 7

 Create a new variable called itu_by_year grouping per "year" and "Income group" variables. Then, remove NAs observations. Later, using the function summarize() you should estimate the median of the Internet value variable and store it in a variable called "medianValue"

```{r}

```


## Pregunta 8

Create a line plot to visualize trends over time. You should use the variables created in the itu_by_year dataset

```{r}

```


## Pregunta 9

Create a new variable called itu_latin filtering per Region, selecting Latin America & Caribbean and grouping per Income group.
Then, using this dataset, create a plot visualizing the relationship between Internet value and GDP (US$) colored per Income group and faceting per Economy

```{r}

```


## Pregunta 10

 Create a new variable called itu_2017 filtering the year 2017 and removing observations that contain NAs.

Then, using this dataset, create a plot visualizing the relationship between Internet value and GDP (US$), colored per Income group. Furthermore, you should use a log scale in both axes ("x" and "y"). Finally, you should use the facet function in order to wrap by Region.

```{r}

```

